A \emph{Grimm} idea

### 2016-04-29 paper/main.tex
added further stuff

% \epigraph{\enquote{Aber, Bruder Wichsstiefel, wo hinaus geht der Weg?} %
%   \enquote{Ich weiß es nicht}, antwortete der Jäger, %
%   \enquote{ich habe mich in dem Wald verirrt.}}%
%   {\emph{Die Stiefel von Büffelleder}\\Brüder Grimm}

@@

\section{Preliminaries}
For the course of this paper we assume the following: Firstly, the vertices can
not be distinguished by the traversing agent. But as the agent moves on a
vertex it can compute its degree. Secondly, the edges attached to the vertex
can be locally distinguished and are enumerated with the indices
$\left\{0,\dots,d_{v}-1\right\}$ where $d_{v}$ denotes the degree of the vertex
$v$. We refer to the \enquote{index} of the edge as its \emph{port}. Note that
every edge thus has two different ports and furthermore that there is no
relation between the ports is assumed. Additionally the degree of the
considered graphs are assumed to be limited by a constant $\Delta$.

@@

In order to describe the movement of an agent we introduce the notion of an
exploration sequence as $e_{0}, e_{1},\dots$ which models relative movements
as follows. We use a sequence of variables $l_{0},l_{1},\dots$ which denotes
the port a vertex was entered through. And the next vertex is determined as the
one connected to the port $(l_{i} + e_{i}) \mod d_{v_{i}}$. We define
$l_{0} = 0$ and the notion $(e_{0},\dots,e_{k})^{\ast}$ for periodic sequences.
It can be shown that a periodic sequence produces a closed walk through a
graph. The proof for this relies on the finiteness of the graph and
\todo{argue why this is a closed walk}

From the result of \cite{logspacealg} which showed that there is a
$\mathcal{O}(\log n)$ algorithm to solve $\mathrm{USTCON}$ and which precisely
states the following:

>>>>

@@

\section{Preliminaries}
For the course of this paper we assume the following: Firstly, the vertices can
not be distinguished by the traversing agent. But as the agent moves on a
vertex it can compute its degree. Secondly, the edges attached to the vertex
can be locally distinguished and are enumerated with the indices
$\left\{0,\dots,d_{v}-1\right\}$ where $d_{v}$ denotes the degree of the vertex
$v$. We refer to the \enquote{index} of the edge as its \emph{port}. Note that
every edge thus has two different ports and furthermore that there is no
relation between the ports is assumed. Additionally the degree of the
considered graphs are assumed to be limited by a constant $\Delta$ and that
there are only a finite amount of vertices.

@@

In order to describe the movement of an agent we introduce the notion of an
exploration sequence as $e_{0}, e_{1},\dots$ which models relative movements
as follows. We use a sequence of variables $l_{0},l_{1},\dots$ which denotes
the port a vertex was entered through. And the next vertex is determined as the
one connected to the port $(l_{i} + e_{i}) \mod d_{v_{i}}$. We define
$l_{0} = 0$ and the notion $(e_{0},\dots,e_{k})^{\ast}$ for periodic sequences.
It can be shown that a periodic sequence produces a closed walk through a
graph. Therefore we argue that there is only a finite amount of triples of the
form $(v,l,i)$ exists where currently the agent is on vertex $v$, entered this
vertex through port $l$ and is currently at index $i$ of the exploration
sequence. For two triples $(v',l',i')$ and $(v'',l'',i'')$ that both lead to
$(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for every
triple there is a unique predecessor and successor which implies due to the
finiteness of the triples $(v,l,i)$ and that the agent moves infinitely it
follows that the first triple has to be valid infinitly often. This means a
periodic exploration sequence yields a closed walk. \todo{maybe enclose in
proof environment}

One result of \cite{logspacealg} states: 
\todo{add theorem boxes and definition boxes}

There is an algorithm $M\in L$ which produces a universal exploration sequence
for every regular graph with $n$ vertices.

From which we can conclude very easily the following Lemma which produces a
universal exploration sequence
